\Huge ACM and Climate Change

### 2019-05-25 main.tex
Progress

The climate crisis is too large and too urgent to just delegate to world
leaders: organizations at every social scale must play their part by addressing
their own contributions, raising awareness among their members, and
establishing new ways of 
doing business in the lower-carbon future that is coming. For ACM, this
especially means developing strategies for reducing the climate impact of
conference-related travel.
%
You can help accelerate this process in a number of ways: 
\begin{itemize}
\item {\bf Get involved} in raising awareness about this issue in the
organizations you are a part of.  \bcp{Does this smack of incrementalism?
  Maybe delete it.
  ``For example, ask the organizers of the conferences you attend what they
  are doing about reducing or offsetting emissions from participants'
  travel.''}
\item {\bf Connect} with others that are engaging with these issues---in
your workplace, in your other communities, and within ACM (e.g., on the
{\tt acm-climate} mailing list~\cite{acm-climate}).
\item {\bf Analyze} your organization's carbon-emitting activities to inform
a discussion of how reduce its footprint and prepare for the era of
expensive carbon.
\end{itemize}

\bcp{Things still missing:
  \begin{itemize}
  \item citations for the claims we make
  \item an excuse for citing the Climate Committee report and perhaps
  mentioning other SIGPLAN activities 
  \end{itemize}
}

>>>>

The climate crisis is too large and too urgent to just delegate to world
leaders: organizations at every social scale must play their part by addressing
their own contributions, raising awareness among their members, and
establishing new ways of 
doing business in the lower-carbon future that is coming. For ACM, this
especially means developing strategies for reducing the climate impact of
conference-related travel.
%
You can help accelerate this process in a number of ways: 
\begin{itemize}
\item {\bf Get involved} in raising awareness about this issue in the
organizations you are a part of.  \bcp{Does this smack of incrementalism?
  Maybe delete it.
  ``For example, ask the organizers of the conferences you attend what they
  are doing about reducing or offsetting emissions from participants'
  travel.''}
\item {\bf Connect} with others that are engaging with these issues---in
your workplace, in your other communities, and within ACM (e.g., on the
{\tt acm-climate} mailing list~\cite{acm-climate}).
\item {\bf Analyze} your organization's carbon-emitting activities to
understand how to reduce its footprint now and prepare for the coming era of
expensive carbon.
\end{itemize}

\bcp{Things still missing:
  \begin{itemize}
  \item citations for the claims we make
  \item an excuse for citing the Climate Committee report and perhaps
  mentioning other SIGPLAN activities
  \item Decide what figures we want, if any
  \item go through all the suggestions below and in the referee reports,
  once more
  \item Write a cover letter
  \begin{itemize}
  \item We tried hard to remove all incrementalism and make it much more
  hard hitting
  \item However, we did keep the suggestion of carbon offsets, hopefully
  in a more convincing / palatable / better argued form
  \item what else?
  \end{itemize}
  \end{itemize}
}
